Accelerating Genetic ANN Training using the CUDA Platform

### 2010-04-18 doc/paper.tex
Rewrite preliminary data processing section, add reference to Duda
git-svn-id: http://svn.scesoc.ca/evolution/trunk@96 fee98b4c-d1c3-4d34-9525-a468159e4a48

% ----------------------------------------------------------------------------
\subsection{Preliminary Data Analysis} \label{prelim}
% ----------------------------------------------------------------------------
Fisher's linear discriminant \cite[\S 3.8.2]{Duda} obtains the 1D projection with best class separation by taking the eigenvector with the highest eigenvalue in a generalized eigenvector problem. We instead took the eigenvectors with the \emph{two} highest eigenvalues and plotted a 2D projection. This showed four defined clusters, which guided our choice of 4 hidden nodes with Gaussian radial basis functions.

>>>>

% ----------------------------------------------------------------------------
\subsection{Preliminary Data Analysis} \label{prelim}
% ----------------------------------------------------------------------------
The maximization of the ratio of between-class scatter to within-class scatter can be posed as a generalized eigenvalue problem where the eigenvalue with the largest corresponding eigenvalue is Fisher's linear discriminant \cite[\S 3.8.2]{Duda}. By taking instead the \emph{two} highest eigenvalues and plotting a 2D projection, we found that the data exhibited 4 defined clusters. This  guided our choice of 4 hidden nodes with Gaussian radial basis functions.
